humanCdGF_predict_cfu

### 2016-10-10 code/HumanCdGF_predict_cfu.Rmd
only plot RSQ for reduced features

heat.plot <- function(input_maxtrix, high_color = '#660000', low_color = '#FFFFFF', legend_title = NA) {
  long.df <- data.frame(input_maxtrix)
  colnames(long.df) <- c(1:10)
  long.df$community_day <- as.character(c(0:10))
  long.df %>% gather(cfu_day, variable, -community_day) %>% 
    ggplot(aes(cfu_day, community_day)) + 
    geom_tile(aes(fill = variable), color = 'white') +
    scale_fill_gradient(low = low_color, high = high_color, name = legend_title) +
    labs(x = 'Day (CFU)', y = 'Day (Community)') + 
    theme(axis.line.x = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank()) + 
    scale_x_discrete(expand = c(0, 0), limits = c('1','2','3','4','5','6','7','8','9','10')) + 
    scale_y_discrete(expand = c(0, 0), limits = c('0','1','2','3','4','5','6','7','8','9','10')) + 
    theme(legend.position = 'top', legend.key.width = unit(2, 'cm'))
}
```

@@

### All OTUs input to Random Forest - without mice euthanized early
```{r all otus, fig.width=10, fig.height=6}
ggdraw()+
  draw_plot(heat.plot(rsq, '#003300', legend_title = expression(paste('R'^'2'))), 0, 0, 0.5, 1) + 
  draw_plot(heat.plot(mse, 'white', '#000066', 'MSE'), 0.5, 0, 0.5, 1)
#plot(otu_votes[otu_votes >= 10], xlab = 'OTU', ylab = 'Freq')
```

@@

```{r top otus, fig.width=10, fig.height=6}

ggdraw()+
  draw_plot(heat.plot(rsq_n, '#003300', legend_title = expression(paste('R'^'2'))), 0, 0, 0.5, 1) + 
  draw_plot(heat.plot(mse_n, 'white', '#000066', 'MSE'), 0.5, 0, 0.5, 1)
#plot(otu_votes_n[otu_votes_n >= 1], xlab = 'OTU', ylab = 'Freq')
```

>>>>

heat.plot <- function(input_maxtrix, high_color = '#660000', low_color = '#FFFFFF', legend_title = NA) {
  long.df <- data.frame(input_maxtrix)
  colnames(long.df) <- c(1:10)
  long.df$community_day <- as.character(c(0:10))
  long.df %>% gather(cfu_day, variable, -community_day) %>% 
    ggplot(aes(cfu_day, community_day)) + 
    geom_tile(aes(fill = variable), color = 'white') +
    scale_fill_gradient(low = low_color, high = high_color, name = legend_title) +
    labs(x = 'Day (CFU)', y = 'Day (Community)') + 
    theme(axis.line.x = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank()) + 
    scale_x_discrete(expand = c(0, 0), limits = c('1','2','3','4','5','6','7','8','9','10')) + 
    scale_y_discrete(expand = c(0, 0), limits = rev(c('0','1','2','3','4','5','6','7','8','9','10'))) + 
    theme(legend.position = 'top', legend.key.width = unit(2, 'cm'))
}
```

@@

### All OTUs input to Random Forest - without mice euthanized early
```{r all otus, fig.width=10, fig.height=6}
heat.plot(rsq, '#003300', legend_title = expression(paste('R'^'2')))
#plot(otu_votes[otu_votes >= 10], xlab = 'OTU', ylab = 'Freq')
```

@@

```{r top otus, fig.width=10, fig.height=6}
heat.plot(rsq_n, '#003300', legend_title = expression(paste('R'^'2')))
#plot(otu_votes_n[otu_votes_n >= 1], xlab = 'OTU', ylab = 'Freq')
```
